Response to reviewers

### 2018-01-31 manuscripts/AmNat_response_to_rev.Rmd
WIP

We appreciate the careful and constructive comments of the editor and reviewers, which have allowed us to re-write the manuscript to both better communicate both the method and broader implications of the results shown here.

@@

we now emphasize that making decisions in face of imperfect information is by no means an issue isolated solely to fisheries, and that our focus on fisheries example is merely for the same reason introductory texts on ecological management have so often turned to fisheries: no other example of ecological managment has a rich or foundational a history in our understanding of ecosystem management and decision-theory.  We now discuss the broader concept of uncertain decision making in the introduction and highlight examples where these issues most readily appear in so many other ecological applications.

> Reviewer 1 in contrast makes a  specific and detailed comment about a very particular issue.   In discussing this comment, an important point is that I am sufficiently far from being a fisheries biologist that I am not entirely understand sure that I understand the objection, emphasizing the importance of Reviewer 2's comment that The American Naturalist is a general interest journal, not a fisheries journal.  This caveat aside, my understanding of Reviewer 1's comment is that the Reviewer ran a set of simulations which were essentially the same as in the manuscript, except that the Reviewer explicitly excluded the possibility of 90 percent harvest of the stock population.  In the reviewer's simulations, the optimal escapement level is lower in the presence of measurement error, whereas in fig. 5 of the manuscript,  the optimal escapement level is instead higher in the presence of measurement error.  Reviewer 1's description of their simulations is brief enough that I would not expect the authors to build their entire revision around an effort to respond to this comment.   If the authors have indeed allowed for 90 percent harvest, however, it is important that they test whether their results are different if they place an upper limit on the fraction of the stock that they allow to be harvested.   I also agree with Reviewer 1's comment that the methods are not that easy to follow.  That said, to my understanding, the escapements in fig. 2 are not constant, and so Reviewer 1's comment that a constant escapement cannot lead to the collapse of a stock seems to me to be irrelevant, but again I may be wrong, and my uncertainty emphasizes the lack of clarity in the writing, especially with respect to the Methods.

The simulations performed by Reviewer 1 are not the same as in our example, but are nevertheless very enlightening as they highlight a very important issue that is far more general than fisheries.  Reviewer 1's simulations have provided another example of the paradox of measurement error that we now highlight much more clearly in the previous work of @Reed1979, @Clark1986, @Sethi2005, and others: Reviewer 1 makes a "simplifying assumption" and paradoxically concludes that in the face of higher measurement error we should increase fishing pressure!  A key conclusion from our analysis is the demonstration that this common but paradoxical claim is in fact false.

To assume harvest cannot exceed the standing stock is to assume (for any model without an Allee threshold) that humans cannot collapse a stock regardless of how hard they fish. Though this assumption that extinction is impossible is often mathematically convenient, we are hardly the first to argue that it is both biologically unrealistic and can lead to ill-advised management practices

> An important tacit assumption in Reed’s analysis, as in the other works referred
to above, is that the recruitment level X is known accurately prior to the harvest decision, [...] In the case of fishery resources, the stock level X is almost never known very accurately, owing to the difficulty of observing fish in their natural environment.

The reviewer's approach is not essentially equivalent to our approach; as the editor already observes we do not assume that the optimal policy will involve constant escapement, nor does it.  Nor is the reviewer's simulation the same as in @Clark1986 or @Sethi2005, since neither of those results involve constant escapement, though they

Reviewer 1 proposes that we assume local extinction is impossible regardless of inaccuracies in measurement error.  This assumption has been previously made in the literature for mathematical convenience, as we discuss it is in fact

When measurements are *uncertain*, it is impossible *not* to allow for a 90% harvest of the stock.  Indeed, this cuts to  the very heart of why measurement uncertainty in *decisions* is so important!  If X is a random number from a log-normal distribution of parameters mu and sigma, how can one choose a number Y to be certain that Y < 90% X?   Y = 0 is the only (non-negative) solution; you cannot be sure that *any* harvest level is guatenteed to be safe.

The editor is absolutely correct, POMDP solutions do not result in a constant escapement, as we stated.  Unfortunately, Reviewer 1 does not provide any description of the methods they used.

We have revised the

@@

We have revised this section significantly to address both grammar and presentation.

The formal definitions and methodology of POMDPs has already been well-documented in the appopriate literature, and there is no reason for us to rehash the all the precise technical details here, which only serves to obscure the most salient concept.  The point here is that there is an immensely well-developed area of theory and tools to address this problem of decision-making under imperfect information.  Though much of that research has come from other fields and is not currently familiar to the readers, we believe we now present enough context to understand the problem.

@@

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.

While based only on this description provided we are not able to precisely replicate Reviewer 1's analysis, we can observe serveral important ways in which it is quite different to the optimization problem we consider.

We have now completely re-written our description and provided both a stand-alone R package and fully executable scripts implementing our methods.  However, we do not attempt to provide a stand-alone introduction to Partially Observed Markov Decision Processes (POMDPs), which, all though less well known in ecology and evolutionary studies than their (fully observed) MDP cousins (which ecologists commonly refer to by their solution method, Stochastic Dynamic Programming or SDP)

As the editor observes, this short discription does not permit us to properly understand what the reviewer has done to obtain
different results, but as the editor already noted, the comments make it clear that it is not analgous to our approach,
since our approach does not assume nor does it find a constant escapement policy to be optimal.  
Moreover, the remark about restricting harvest to 90% of population size is very instructive, as it cuts to the heart of the problem of measurement uncertainty. 
Clearly such a restriction is only possible if the manager has access to perfect observations of the stock size,
an thus any simulation that enforces this restriction is implicitly ignoring the reality of measurement error.

There are only two ways a manager can be certain that harvest does not exceed 90% of stock: (1) don't harvest, or (2) measure the stock size exactly, (or at least, exactly measure some absolute lower bound of possible stock sizes).

As the literature has observed consistently for some time, (e.g. see an eloquent discussion in Clark & Kirkwood 1987) 
if we only consider policies in which accidental population extinction by overharvesting is impossible, 
(e.g. because we assume a priori harvest cannot exceed 90% of the stock), 
there is every reason to suspect this will result in artifically less cautious policies.  If we begin with 
the assumption that there's just no possible way overharvesting could destroy a stock, then the risks of
overharvesting are drastically reduced: net present value need only reflect the loss of revenue while a stock
rebuilds, and not the much greater loss that would result from extinction.  Because even the stochastic theory
such as Reed 1979 made effectively the same assumption (e.g. assumes the stock is measured perfectly before
harvest, so that it would never be rational to attempt a harvest)

@@

As we discuss above, this is once again fundamental feature of measurement uncertainty -- and again one
that was observed long before our paper and is well established by the literature we discuss at some length.
If a fixed escapement policy is applied to a measurement that is uncertain, the true stock will be somewhat
larger or somewhat smaller than the observed value, and thus the true escapement can be somewhat smaller
or somewhat larger than the 'target' escapement.  Without perfect measurements, it is clearly impossible
to achieve the target escapement exactly. If, by chance, a string of consecutive measurements repeatedly over-estimates
the current stock size, a constant-escapement strategy will repeatedly over-harvest the stock.

In a model without an Allee effect, such as the classic Gordon-Schaefer model we focus on here, successive over-harvesting
can reduce a stock to an

The novelty of our result is how to deal with this issue.

@@

-- while a rigorous constant escapement policy shuts down
all harvest below B_MSY (the constant escapement level), most fisheries actually continue to harvest
even when the stock drops below the target stock size, though potentially at some decreasing rate,
and do not shut down harvest until the population is significantly below this level, commonly B_MSY / 2, if at all.

As mentioned above, we have now revised all of our analyses to consider these realistic harvest policies,
and have added a substantial discussion addressing the differences between such constant harvest (or constant effort /
fishing mortality) policies and the constant-escapement policies we have hitherto focused upon.  
Because these policies permit harvesting below B_MSY, it is not surprising that we find them even more
suseptible

@@

We thank the reviewer for this careful and constructive review, and agree entirely with the recommendation that the fundamental issues here (managing with imperfect information) as well as some other themes (tipping points, management with constrained resources) are far more general. We have now tried to state these implications more clearly.

@@

This is an excellent point which we now develop in the discussion:

How do we determine the maximum sustainable yield in the first place?  This number comes from a deterministic stock-recruitment model.  In stochastic models, and even in many deterministic models with age and stage structure, there is no such thing as a maximum sustainable yield, since the optimal yield must fluctuate with the population dynamics.  But at least in those cases one can reasonably assert an average

@@

 As the reviewer suggests here and as was recognized by Fischer et al (2009) among others, one advantage of the optimal control approach is that it is generally more transparent and unbiased algorithmic way to reach a decision, which to some extent sidesteps the inherently more subjective existing methods, where this issue is acutely felt.  For instance, our value function is a cold-blooded profit equation which places no value in leaving fish in the sea beyond their future return as harvest.  We also ignore more realistic supply-and-demand effects as a conservative assumption, since the decreasing price of higher supply would dampen the incentive for larger harvests (see comparisons in appendix).

@@

Excellent observation! We have added the following line to emphasize this more clearly:

@@

@@

Agreed.

@@

>>>>

We appreciate the careful and constructive comments of the editor and reviewers, which have allowed us to re-write the manuscript to address each of the issues raised here.

Reviewer 1's primary objection essentially re-asserts the "paradox of measurement uncertainty" that previous literature has also asserted: that uncertainty should somehow make less cautious.  We appreciate the reviewer highlighting the importance of explaning this central issue properly, and our revisions should make it clear how this erroneous and potentially dangerous conclusion arises from simplifying assumptions.  Reviewer 2's primary objection is the missed opportunity of focusing too narrowly on fisheries.  We agree entirely with the reviewer that the fundamental issues here are germane to ecological management and not specific to fisheries, and have revised the presentation substantially to address this.  Both reviewers raised concerns about the clarity of the methods; so in addition to rewritten discussion of methods we now provide fully executable code to replicate the analysis shown here.  Lastly but most importantly, both reviewers raise the observation that few fisheries are actually managed using a strict constant escapement (CE) policy.  We have introduced more realistic management strategies based on regulating fishing mortality through maximum sustainable yield (MSY) and total allowable catch (TAC), as additional comparisions.  TAC illustrates a different, more heuristic approach to uncertainty than seen in the optimal control methods that provides some valuable additional insights into the challenge of accounting for measurement error. We think this results in a much more interesting mansucript which should be relevant to the broad audience of the American Naturalist.

Below we provide more detailed responses to each of the concerns raised and how they have been addressed in this revision.

@@

We now emphasize that making decisions in face of imperfect information is by no means an issue isolated solely to fisheries, which merely serves as a concrete example where relevant data can be easily obtained.  We also note that fisheries management has long been a crucible in which ecological management theory and practice has been forged before becoming widely applied in other ecological contexts.

> Reviewer 1 in contrast makes a  specific and detailed comment about a very particular issue.   In discussing this comment, an important point is that I am sufficiently far from being a fisheries biologist that I am not entirely understand sure that I understand the objection, emphasizing the importance of Reviewer 2's comment that The American Naturalist is a general interest journal, not a fisheries journal.  This caveat aside, my understanding of Reviewer 1's comment is that the Reviewer ran a set of simulations which were essentially the same as in the manuscript, except that the Reviewer explicitly excluded the possibility of 90 percent harvest of the stock population.

The analysis of Reviewer 1 is very interesting, and finds essentially the same paradoxical result as earlier published studies (e.g. @Clark1986; @Sethi2005); as the reviewer summarizes:

> In every case the optimal escapement goal was lower when observation error was included.

This is a paradoxical conclusion that defies the precautionary principle, and as such would have important ramifications in ecological management in many applications beyond fisheries.  Further, though the reviewer's analysis is not identical to either the approaches of @Clark1986 or @Sethi2005 (neither assume constant escapement and both find this paradoxical result in only some but not all cases), we believe our analysis provides both a refutation of this result and a clear intutition as to where this misleading conclusion has come from.

As the editor notes, we suspect that Reviewer 1's simulations are not indeed identical except in the way mentioned, since they appear to assume the optimal policy can be specified in terms of a single constant escapement. Our results and in general escapement need not be constant but will depend on the observed stock size an on previous measurements, as we now emphasize.  Also as the editor notes, the Reviewer's description of what they have done is extremely brief and thus difficult to be sure we have characterized precisely, but nevertheless, we believe our analysis sheds some light on why the reviewer finds this paradoxical conclusion while our analysis does not.

The escapement recommended by our POMDP solution is not constant, but depends both on prior information and the current estimate of the stock size, as illustrated in Figure 4.  Assumptions that simplify the calculation of the policy by ignoring these aspects can thus reach different conclusions.  @Clark1986 assumes that the stock size is known perfectly at the end of the prior period, @Sethi2005 implicitly assumes that the prior belief is always uniform rather than reflecting previous measurements, which puts erroneous probability weight on the chance the stock is in fact very high.

Figure 4 offers a clear explanation for when it is optimal to increase harvest in response to increased uncertainty: the POMDP harvest only exceeds the CE harvest when the measured stock size is erroneously low.  That is, when the prior belief would have suggested the observation should be much higher, and therefore the measurement is most likely an error under-estimating the true stock size.  This logic is entirely intuitive and is bourne out in the resulting POMDP policies.

>  In the reviewer's simulations, the optimal escapement level is lower in the presence of measurement error, whereas in fig. 5 of the manuscript,  the optimal escapement level is instead higher in the presence of measurement error.  Reviewer 1's description of their simulations is brief enough that I would not expect the authors to build their entire revision around an effort to respond to this comment.   If the authors have indeed allowed for 90 percent harvest, however, it is important that they test whether their results are different if they place an upper limit on the fraction of the stock that they allow to be harvested.

The reviewer and editor have raised an important issue in the question of whether we permit the harvest quota to be set to a value higher than the stock.  There are two problems with this.  First, it's not clear how the reviewer implements this assumption in the face of measurement uncertainty: how can one be certain a quota is less than 90% of stock size X without knowing what X is?  One can obviously enforce this with respect to the measured stock size but not the true stock size.  More importantly, this assumption amounts to the assertion that it is mathematically impossible to overfish a stock to the point of collapse.  However low the stock size might get, local extinction is impossible.  In this world-view, there will always be some tiny fraction of ato-fishes from which the population can recover.  Assuming that local extinction is impossible will indeed bias any optimal decision model to be more agressive.  Obviously this also has impliciations for ecological models in general, conservation policy would look different if we assumed extinction was impossible. @Clark1986 already recognized that a very similar assumption in @Reed1979 derivation that stochastic models needed no additional caution ($S=D$) was likely due to the fact that accidentally extinction was impossible (see manuscript, line 150). We do not adopt this assumption.  Obviously real world populations cannot be indefinitely reduced by only a fractional percentage. In our simulations, though we consider a Ricker model, stock abundances are divided into 100 distinct bins, with the smallest bin corresponding to a stock size of zero. Thus it is possible for overharvesting or stochastic environment, or some combination of both, to lead a population to permanenently collapse once it has gotten small enough.

> I also agree with Reviewer 1's comment that the methods are not that easy to follow.  That said, to my understanding, the escapements in fig. 2 are not constant, and so Reviewer 1's comment that a constant escapement cannot lead to the collapse of a stock seems to me to be irrelevant, but again I may be wrong, and my uncertainty emphasizes the lack of clarity in the writing, especially with respect to the Methods.

We agree entirely with this, and hope that the rewritten description, together with complete code, helps make this somewhat clearer.

@@

The presentation of all of this material has been entirely re-written in what we hope you will find is a much more appropriate and accessible style.  To avoid needless formalism, we do not rehash the technical details of solving Partially Observed Markov Decision Processes but instead point to the extensive literature already existing on the subject.  Instead, we focus on describing the nature of the problem and how it differs from analyses such as the perfectly observed Markov Decision Process that provides the basis for the Constant Escapement strategy (@Reed1979) and from other Bayesian hierarchical modeling (e.g. partially observed Markov processes, pomp, or Hidden Markov Models, HMMs) which are not decisison processes at all, but rather a prerequiste part of choosing & paramaterizing a model, not using said model to make a decision.

@@

> The graph below shows a typical result. The thin line is with no observation error, the ticker line with the observation error. In every case the optimal escapement goal was lower when observation error was included.

We thank the Reviewer for this careful parallel investigation, which was very useful in focusing the manuscript on some of the key results.  We believe the differences in our respective results can be explained by the differences in our methods as discussed in our reply to the Editor's discussion of this issue. In short, we believe the reviewer's seemingly counter-intuitive result that increased uncertainty should be met with an action (lowering escapement) that would increase the risk of stock collapse rather then the intuitive response to be cautious by reducing harvest, is simply an artefact of the reviewer's assumption that stock collapse is impossible, and thus increased harvesting poses no real risk.

@@

We agree that the results and methodoloy could have been much more clearly presented. We hope the rewritten presentation of these results clarifies these issues. In particular, note that once you introduce measurement error a fixed escapement policy can only achieve a fixed *expected* escapement, you never know what the actual escapement is because you never know exactly how many fish you started with.  As measurement errors are equally likely to be too high or too low, a run of "heads", so to speak, would result in consistently overharvesting and continued decline (see discussion around line 363.)

@@

@@

We thank the reviewer for this careful and constructive review, and agree entirely with the recommendation that the fundamental issues here are not limited to the problem of fishing quotas butare germane to much of ecological decision making. We have now tried both to set up the generic nature of the issue of measurement uncertainty (see Introduction) and discuss its implications beyond fisheries much more explicitly (e.g. lines 423 - 437).  We have however removed the treatment of the tipping point model in order to focus explicitly on the role of uncertainty in the more familiar case of logistic growth, where the dramatic consequences of measurement uncertainty may be less inutitive and cannot be dismissed merely by questioning the frequency of tipping points occurring in real systems.  We hope to address the problem of tipping points more explicitly and more fully in later work.

@@

This is an excellent point which we now develop in the discussion, lines 456-470.

@@

We now include a formal comparison against TAC-based management policy (and also MSY based policy in the supplement), which reflect this aspect of today's actual management polcies which are not updated annually but apply a constant fishing effort (mortality). We also discuss several of the practical objections to implementing POMDP in practice and how it might be modified to address more of these concerns, e.g. lines 456-490.

@@

Excellent observation! Yes, due to the influence of the prior belief, POMDP is slightly more catious when a stock is rebuilding from small sizes

@@

We agree entirely, and now present the full discussion of the methods and models before going into the results.

@@

Agreed, this has been addressed in the rewrite.

@@

We believe this is much better illustrated by the visualization of these solutions in Figure 5, and introducing a statistic to quantify this would only needlessly confuse that discussion.
